---
title: "WANDA Priorities"
output: pdf_document
date: "2025-09-10"
---

This is an RMarkdown document summarising the quantitative data analysis for the WANDA Priorities Paper.

# SETTING UP ENVIRONMENT
Loading the packages I use most. Suppressing messages from appearing in RMarkdown doc, so they do not take up space.
```{r results="hide", warning=FALSE, comment=FALSE, message=FALSE}
library(ggplot2)
library(janitor)
library(dplyr)
library(writexl)
library(psych)
library(Hmisc)
library(plyr)
library(ggExtra)
library(doBy)
library(grid)
```

Turn off scientific notation
```{r}
options(scipen=999) 
```

Set theme for future plots
```{r}
theme_set(
        theme_minimal((base_size = 16)) +
                theme(legend.position = "right"))
```

Preparing the data: This sets up the R environment and ensures readr is installed/loaded and configuring knitr to display code in the output.
```{r setup, include=FALSE}
options(repos = c(CRAN = "https://cran.r-project.org"))
if (!requireNamespace("readr", quietly = TRUE)) {
  install.packages("readr")
}
library(readr)

knitr::opts_chunk$set(echo = TRUE)
```

Checking R version
```{r}
R.version
```

Loading dataset
```{r}
WANDA <- read.csv("MERGED_MOTHERS_USE_2_TOSHARE_CLEANED_300625.csv", header=TRUE, na.string=c("","NA", " ", "not known", "-997", "-998","-999", "-996"))
```

```{r}
str(WANDA)
```

DEMOGRAPHICS 

```{r}
psych::describe(WANDA$Q1_AgeYears)
```

Frequencies for diagnosis autism 
```{r}
table(WANDA$Q1_4_DiagnosisAutism)
```

Manual checks
How many yes autism
```{r}
32+54
```

Percentage yes autism
```{r}
8600/709
```

How many yes and maybes autism
```{r}
54+32+77
```

Percentage autism yes and maybe
```{r}
(163*100)/709
```

Frequencies for diagnosis ADHD 
```{r}
table(WANDA$Q1_3_DiagnosisADHD)
```

Manual checks
How many yeses
```{r}
31+73
```

Percentage yeses
```{r}
10400/709
```

How many including maybes
```{r}
104+89
```

Percentage including maybes
```{r}
19300/709
```

Frequencies for diagnosis other NDCs
```{r}
table(WANDA$Q1_6_DiagnosisOtherNeurodev)
```

Manual checks
How many yeses
```{r}
67+15
```

Percentage yeses
```{r}
8200/709
```

Numbers including maybe
```{r}
82+23
```

Percentage including maybe
```{r}
10500/709
```



Frequencies for diagnosis depression 

```{r}
table(WANDA$Q1_1_DiagnosisDepression)
```

Manual checks
Frequency for depression yes
```{r}
70+302
```

Percentages for depression
```{r}
37200/709
```

Frequencies for depresssion yes and maybe
```{r}
372+59
```

Percentages
```{r}
43100/709
```

Frequencies for diagnosis anxiety
```{r}
table(WANDA$Q1_2_DiagnosisAnxiety)
```

Manual checks
Frequency yes anxiety
```{r}
315+109
```

Percentages
```{r}
42400/709
```

Plus maybes
```{r}
424+83
```

Percentages
```{r}
50700/709
```

Frequencies for diagnosis other mental health conditions
```{r}
table(WANDA$Q1_5_DiagnosisOtherMentalHealth)
```
Frequency yes
```{r}
108+44
```

Percentage yes
```{r}
15200/709
```

Frequency plus maybes
```{r}
152+38
```

Percentages
```{r}
19000/709
```


Other demographics
```{r}
tabyl(WANDA$Q2_GenderIdentity)
```
```{r}
tabyl(WANDA$Q3_SexualOrientation)
```
```{r}
tabyl(WANDA$Q4_RaceEthnicity)
```

Manual check
```{r}
.8222+.0013+.0028+.0789+.0028
```

Education
```{r}
tabyl(WANDA$Q5_Education)
```

Manual check
```{r}
.4542+.3681
```

Relationship status
```{r}
tabyl(WANDA$Q4_RelationshipStatus)
```

Manual check
```{r}
.2426+.7151
```

Pregnancy status
```{r}
tabyl(WANDA$Q3_YouPregnant)
```

Manual check
```{r}
.1368+.0522
```

Pregnancy during covid
```{r}
tabyl(WANDA$Q5_PregnancyDuringCovid)
```

Manual check
```{r}
.1594+.1608
```

CREATING SUBSETS OF DATAFRAMES 

NEURODIVERGENT SAMPLE 
Subset: any variable where the answwer is Yes / Likely Yes, and none are "Prefer not to answer"
```{r}
WANDA_NDC <- subset(
  WANDA,
  (Q1_4_DiagnosisAutism %in% c(
     "YES, I have been diagnosed with this",
     "YES/LIKELY YES. I have never received a diagnosis but this applies to me / I self-identity with this"
   ) |
   Q1_3_DiagnosisADHD %in% c(
     "YES, I have been diagnosed with this",
     "YES/LIKELY YES. I have never received a diagnosis but this applies to me / I self-identity with this"
   ) |
   Q1_6_DiagnosisOtherNeurodev %in% c(
     "YES, I have been diagnosed with this",
     "YES/LIKELY YES. I have never received a diagnosis but this applies to me / I self-identity with this"
   ))
)
```



Check structure
```{r}
str(WANDA_NDC)
```

How many people ranked each in top 5 and mean rank
```{r}
tabyl(WANDA$Q4_1_RankPrevalence)
```

```{r}
709-523
```

```{r}
18600/709
```

```{r}
psych::describe(WANDA$Q4_1_RankPrevalence)
```



```{r}
tabyl(WANDA$Q4_8_RankInterventionsWomen)
```

```{r}
709-197
```

```{r}
51200/709
```

```{r}
psych::describe(WANDA$Q4_8_RankInterventionsWomen)
```



```{r}
tabyl(WANDA$Q4_2_RankDiagnosisWomen)
```

```{r}
709-298
```

```{r}
41100/709
```

```{r}
psych::describe(WANDA$Q4_2_RankDiagnosisWomen)
```



```{r}
tabyl(WANDA$Q4_15_RankParentParentRel)
```

```{r}
709-513
```

```{r}
19600/709
```

```{r}
psych::describe(WANDA$Q4_15_RankParentParentRel)
```



```{r}
tabyl(WANDA$Q4_14_RankParentInfantRel)
```

```{r}
709-322
```

```{r}
38700/709
```

```{r}
psych::describe(WANDA$Q4_14_RankParentInfantRel)
```



```{r}
tabyl(WANDA$Q4_10_RankHealthOutcomesWomen)
```

```{r}
709-415
```

```{r}
29400/709
```

```{r}
psych::describe(WANDA$Q4_10_RankHealthOutcomesWomen)
```



```{r}
tabyl(WANDA$Q4_12_RankHealthOutcomesBaby)
```

```{r}
709-436
```

```{r}
27300/709
```

```{r}
psych::describe(WANDA$Q4_12_RankHealthOutcomesBaby)
```



```{r}
tabyl(WANDA$Q4_7_RankProtectiveFactors)
```

```{r}
709-446
```

```{r}
26300/709
```

```{r}
psych::describe(WANDA$Q4_7_RankProtectiveFactors)
```



```{r}
tabyl(WANDA$Q4_6_RankPreviousPregnancies)
```

```{r}
709-476
```

```{r}
23300/709
```

```{r}
psych::describe(WANDA$Q4_6_RankPreviousPregnancies)
```



```{r}
tabyl(WANDA$Q4_5_RankEnvironmentalRisk)
```

```{r}
709-517
```

```{r}
19200/709
```

```{r}
psych::describe(WANDA$Q4_5_RankEnvironmentalRisk)
```



```{r}
tabyl(WANDA$Q4_4_RankBiologicalRisk)
```

```{r}
709-555
```

```{r}
15400/709
```

```{r}
psych::describe(WANDA$Q4_4_RankBiologicalRisk)
```



```{r}
tabyl(WANDA$Q4_3_RankDiagnosisPartners)
```

```{r}
709-554
```

```{r}
15500/709
```

```{r}
psych::describe(WANDA$Q4_3_RankDiagnosisPartners)
```



```{r}
tabyl(WANDA$Q4_9_RankInterventionsPartners)
```

```{r}
709-560
```

```{r}
14900/709
```

```{r}
psych::describe(WANDA$Q4_9_RankInterventionsPartners)
```



```{r}
tabyl(WANDA$Q4_13_RankSocialEconomic)
```

```{r}
709-601
```

```{r}
10800/709
```

```{r}
psych::describe(WANDA$Q4_13_RankSocialEconomic)
```



```{r}
tabyl(WANDA$Q4_11_RankHealthOutcomesPartners)
```

```{r}
709-677
```

```{r}
3200/709
```

```{r}
psych::describe(WANDA$Q4_11_RankHealthOutcomesPartners)
```



Repeating above for NDC subsample 
```{r}
tabyl(WANDA_NDC$Q4_1_RankPrevalence)
```

```{r}
212-146
```

```{r}
6600/212
```

```{r}
psych::describe(WANDA_NDC$Q4_1_RankPrevalence)
```



```{r}
tabyl(WANDA_NDC$Q4_8_RankInterventionsWomen)
```

```{r}
212-55
```

```{r}
15700/212
```

```{r}
psych::describe(WANDA_NDC$Q4_8_RankInterventionsWomen)
```


```{r}
tabyl(WANDA_NDC$Q4_2_RankDiagnosisWomen)
```

```{r}
212-89
```

```{r}
12300/212
```

```{r}
psych::describe(WANDA_NDC$Q4_2_RankDiagnosisWomen)
```



```{r}
tabyl(WANDA_NDC$Q4_15_RankParentParentRel)
```

```{r}
212-152
```

```{r}
6000/212
```

```{r}
psych::describe(WANDA_NDC$Q4_15_RankParentParentRel)
```



```{r}
tabyl(WANDA_NDC$Q4_14_RankParentInfantRel)
```

```{r}
212-94
```

```{r}
11800/212
```

```{r}
psych::describe(WANDA_NDC$Q4_14_RankParentInfantRel)
```



```{r}
tabyl(WANDA_NDC$Q4_10_RankHealthOutcomesWomen)
```

```{r}
212-134
```

```{r}
7800/212
```

```{r}
psych::describe(WANDA_NDC$Q4_10_RankHealthOutcomesWomen)
```


```{r}
tabyl(WANDA_NDC$Q4_12_RankHealthOutcomesBaby)
```

```{r}
212-131
```

```{r}
8100/212
```

```{r}
psych::describe(WANDA_NDC$Q4_12_RankHealthOutcomesBaby)
```



```{r}
tabyl(WANDA_NDC$Q4_7_RankProtectiveFactors)
```

```{r}
212-132
```

```{r}
8000/212
```

```{r}
psych::describe(WANDA_NDC$Q4_7_RankProtectiveFactors)
```



```{r}
tabyl(WANDA_NDC$Q4_6_RankPreviousPregnancies)
```

```{r}
212-149
```

```{r}
6300/212
```

```{r}
psych::describe(WANDA_NDC$Q4_6_RankPreviousPregnancies)
```



```{r}
tabyl(WANDA_NDC$Q4_5_RankEnvironmentalRisk)
```

```{r}
212-159
```

```{r}
5300/212
```

```{r}
psych::describe(WANDA_NDC$Q4_5_RankEnvironmentalRisk)
```



```{r}
tabyl(WANDA_NDC$Q4_4_RankBiologicalRisk)
```

```{r}
212-168
```

```{r}
4400/212
```

```{r}
psych::describe(WANDA_NDC$Q4_4_RankBiologicalRisk)
```



```{r}
tabyl(WANDA_NDC$Q4_3_RankDiagnosisPartners)
```

```{r}
212-160
```

```{r}
5200/212
```

```{r}
psych::describe(WANDA_NDC$Q4_3_RankDiagnosisPartners)
```



```{r}
tabyl(WANDA_NDC$Q4_9_RankInterventionsPartners)
```

```{r}
212-172
```

```{r}
4000/212
```

```{r}
psych::describe(WANDA_NDC$Q4_9_RankInterventionsPartners)
```

```{r}
tabyl(WANDA_NDC$Q4_13_RankSocialEconomic)
```

```{r}
212-176
```

```{r}
3600/212
```

```{r}
psych::describe(WANDA_NDC$Q4_13_RankSocialEconomic)
```

```{r}
tabyl(WANDA_NDC$Q4_11_RankHealthOutcomesPartners)
```

```{r}
212-203
```

```{r}
900/212
```

```{r}
psych::describe(WANDA_NDC$Q4_11_RankHealthOutcomesPartners)
```


Calculating priority scores

```{r}
str(WANDA$Q4_1_RankPrevalence)
```

```{r}
WANDA$Q4_1_RankPrevalenceREV <- recode(WANDA$Q4_1_RankPrevalence,
                                       `1` = 5,
                                       `2` = 4,
                                       `3` = 3,
                                       `4` = 2,
                                       `5` = 1)
```

```{r}
Q4_1_RankPrevalenceSUM <- sum(WANDA$Q4_1_RankPrevalenceREV, na.rm = TRUE)
Q4_1_RankPrevalenceSUM
```

Now listing all variables that contain "rank"
```{r}
vars <- grep("Rank", names(WANDA), value = TRUE)
print(vars)
```

Running the code for all of them to reverse score
```{r}
WANDA$Q4_2_RankDiagnosisWomenREV <- recode(WANDA$Q4_2_RankDiagnosisWomen,
                                           `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_2_RankDiagnosisWomenSUM <- sum(WANDA$Q4_2_RankDiagnosisWomenREV, na.rm = TRUE)
Q4_2_RankDiagnosisWomenSUM
```


```{r}
WANDA$Q4_3_RankDiagnosisPartnersREV <- recode(WANDA$Q4_3_RankDiagnosisPartners,
                                              `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_3_RankDiagnosisPartnersSUM <- sum(WANDA$Q4_3_RankDiagnosisPartnersREV, na.rm = TRUE)
Q4_3_RankDiagnosisPartnersSUM
```

```{r}
WANDA$Q4_4_RankBiologicalRiskREV <- recode(WANDA$Q4_4_RankBiologicalRisk,
                                           `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_4_RankBiologicalRiskSUM <- sum(WANDA$Q4_4_RankBiologicalRiskREV, na.rm = TRUE)
Q4_4_RankBiologicalRiskSUM
```

```{r}
WANDA$Q4_5_RankEnvironmentalRiskREV <- recode(WANDA$Q4_5_RankEnvironmentalRisk,
                                              `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_5_RankEnvironmentalRiskSUM <- sum(WANDA$Q4_5_RankEnvironmentalRiskREV, na.rm = TRUE)
Q4_5_RankEnvironmentalRiskSUM
```

```{r}
WANDA$Q4_6_RankPreviousPregnanciesREV <- recode(WANDA$Q4_6_RankPreviousPregnancies,
                                                `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_6_RankPreviousPregnanciesSUM <- sum(WANDA$Q4_6_RankPreviousPregnanciesREV, na.rm = TRUE)
Q4_6_RankPreviousPregnanciesSUM
```

```{r}
WANDA$Q4_7_RankProtectiveFactorsREV <- recode(WANDA$Q4_7_RankProtectiveFactors,
                                              `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_7_RankProtectiveFactorsSUM <- sum(WANDA$Q4_7_RankProtectiveFactorsREV, na.rm = TRUE)
Q4_7_RankProtectiveFactorsSUM
```

```{r}
WANDA$Q4_8_RankInterventionsWomenREV <- recode(WANDA$Q4_8_RankInterventionsWomen,
                                               `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_8_RankInterventionsWomenSUM <- sum(WANDA$Q4_8_RankInterventionsWomenREV, na.rm = TRUE)
Q4_8_RankInterventionsWomenSUM
```

```{r}
WANDA$Q4_9_RankInterventionsPartnersREV <- recode(WANDA$Q4_9_RankInterventionsPartners,
                                                  `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_9_RankInterventionsPartnersSUM <- sum(WANDA$Q4_9_RankInterventionsPartnersREV, na.rm = TRUE)
Q4_9_RankInterventionsPartnersSUM
```

```{r}
WANDA$Q4_10_RankHealthOutcomesWomenREV <- recode(WANDA$Q4_10_RankHealthOutcomesWomen,
                                                 `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_10_RankHealthOutcomesWomenSUM <- sum(WANDA$Q4_10_RankHealthOutcomesWomenREV, na.rm = TRUE)
Q4_10_RankHealthOutcomesWomenSUM
```

```{r}
WANDA$Q4_11_RankHealthOutcomesPartnersREV <- recode(WANDA$Q4_11_RankHealthOutcomesPartners,
                                                    `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_11_RankHealthOutcomesPartnersSUM <- sum(WANDA$Q4_11_RankHealthOutcomesPartnersREV, na.rm = TRUE)
Q4_11_RankHealthOutcomesPartnersSUM
```

```{r}
WANDA$Q4_12_RankHealthOutcomesBabyREV <- recode(WANDA$Q4_12_RankHealthOutcomesBaby,
                                                `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_12_RankHealthOutcomesBabySUM <- sum(WANDA$Q4_12_RankHealthOutcomesBabyREV, na.rm = TRUE)
Q4_12_RankHealthOutcomesBabySUM
```

```{r}
WANDA$Q4_13_RankSocialEconomicREV <- recode(WANDA$Q4_13_RankSocialEconomic,
                                            `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_13_RankSocialEconomicSUM <- sum(WANDA$Q4_13_RankSocialEconomicREV, na.rm = TRUE)
Q4_13_RankSocialEconomicSUM
```

```{r}
WANDA$Q4_14_RankParentInfantRelREV <- recode(WANDA$Q4_14_RankParentInfantRel,
                                             `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_14_RankParentInfantRelSUM <- sum(WANDA$Q4_14_RankParentInfantRelREV, na.rm = TRUE)
Q4_14_RankParentInfantRelSUM
```

```{r}
WANDA$Q4_15_RankParentParentRelREV <- recode(WANDA$Q4_15_RankParentParentRel,
                                             `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_15_RankParentParentRelSUM <- sum(WANDA$Q4_15_RankParentParentRelREV, na.rm = TRUE)
Q4_15_RankParentParentRelSUM
```


Now same for the NDC subsample

```{r}
WANDA_NDC$Q4_1_RankPrevalenceREV <- recode(WANDA_NDC$Q4_1_RankPrevalence,
                                       `1` = 5,
                                       `2` = 4,
                                       `3` = 3,
                                       `4` = 2,
                                       `5` = 1)
Q4_1_RankPrevalenceSUMNDC <- sum(WANDA_NDC$Q4_1_RankPrevalenceREV, na.rm = TRUE)
Q4_1_RankPrevalenceSUMNDC
```

```{r}
WANDA_NDC$Q4_2_RankDiagnosisWomenREV <- recode(WANDA_NDC$Q4_2_RankDiagnosisWomen,
                                           `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_2_RankDiagnosisWomenSUMNDC <- sum(WANDA_NDC$Q4_2_RankDiagnosisWomenREV, na.rm = TRUE)
Q4_2_RankDiagnosisWomenSUMNDC
```

```{r}
WANDA_NDC$Q4_3_RankDiagnosisPartnersREV <- recode(WANDA_NDC$Q4_3_RankDiagnosisPartners,
                                              `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_3_RankDiagnosisPartnersSUMNDC <- sum(WANDA_NDC$Q4_3_RankDiagnosisPartnersREV, na.rm = TRUE)
Q4_3_RankDiagnosisPartnersSUMNDC
```

```{r}
WANDA_NDC$Q4_4_RankBiologicalRiskREV <- recode(WANDA_NDC$Q4_4_RankBiologicalRisk,
                                           `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_4_RankBiologicalRiskSUMNDC <- sum(WANDA_NDC$Q4_4_RankBiologicalRiskREV, na.rm = TRUE)
Q4_4_RankBiologicalRiskSUMNDC
```

```{r}
WANDA_NDC$Q4_5_RankEnvironmentalRiskREV <- recode(WANDA_NDC$Q4_5_RankEnvironmentalRisk,
                                              `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_5_RankEnvironmentalRiskSUMNDC <- sum(WANDA_NDC$Q4_5_RankEnvironmentalRiskREV, na.rm = TRUE)
Q4_5_RankEnvironmentalRiskSUMNDC
```

```{r}
WANDA_NDC$Q4_6_RankPreviousPregnanciesREV <- recode(WANDA_NDC$Q4_6_RankPreviousPregnancies,
                                                `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_6_RankPreviousPregnanciesSUMNDC <- sum(WANDA_NDC$Q4_6_RankPreviousPregnanciesREV, na.rm = TRUE)
Q4_6_RankPreviousPregnanciesSUMNDC
```

```{r}
WANDA_NDC$Q4_7_RankProtectiveFactorsREV <- recode(WANDA_NDC$Q4_7_RankProtectiveFactors,
                                              `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_7_RankProtectiveFactorsSUMNDC <- sum(WANDA_NDC$Q4_7_RankProtectiveFactorsREV, na.rm = TRUE)
Q4_7_RankProtectiveFactorsSUMNDC
```

```{r}
WANDA_NDC$Q4_8_RankInterventionsWomenREV <- recode(WANDA_NDC$Q4_8_RankInterventionsWomen,
                                               `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_8_RankInterventionsWomenSUMNDC <- sum(WANDA_NDC$Q4_8_RankInterventionsWomenREV, na.rm = TRUE)
Q4_8_RankInterventionsWomenSUMNDC
```

```{r}
WANDA_NDC$Q4_9_RankInterventionsPartnersREV <- recode(WANDA_NDC$Q4_9_RankInterventionsPartners,
                                                  `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_9_RankInterventionsPartnersSUMNDC <- sum(WANDA_NDC$Q4_9_RankInterventionsPartnersREV, na.rm = TRUE)
Q4_9_RankInterventionsPartnersSUMNDC
```

```{r}
WANDA_NDC$Q4_10_RankHealthOutcomesWomenREV <- recode(WANDA_NDC$Q4_10_RankHealthOutcomesWomen,
                                                 `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_10_RankHealthOutcomesWomenSUMNDC <- sum(WANDA_NDC$Q4_10_RankHealthOutcomesWomenREV, na.rm = TRUE)
Q4_10_RankHealthOutcomesWomenSUMNDC
```

```{r}
WANDA_NDC$Q4_11_RankHealthOutcomesPartnersREV <- recode(WANDA_NDC$Q4_11_RankHealthOutcomesPartners,
                                                    `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_11_RankHealthOutcomesPartnersSUMNDC <- sum(WANDA_NDC$Q4_11_RankHealthOutcomesPartnersREV, na.rm = TRUE)
Q4_11_RankHealthOutcomesPartnersSUMNDC
```

```{r}
WANDA_NDC$Q4_12_RankHealthOutcomesBabyREV <- recode(WANDA_NDC$Q4_12_RankHealthOutcomesBaby,
                                                `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_12_RankHealthOutcomesBabySUMNDC <- sum(WANDA_NDC$Q4_12_RankHealthOutcomesBabyREV, na.rm = TRUE)
Q4_12_RankHealthOutcomesBabySUMNDC
```

```{r}
WANDA_NDC$Q4_13_RankSocialEconomicREV <- recode(WANDA_NDC$Q4_13_RankSocialEconomic,
                                            `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_13_RankSocialEconomicSUMNDC <- sum(WANDA_NDC$Q4_13_RankSocialEconomicREV, na.rm = TRUE)
Q4_13_RankSocialEconomicSUMNDC
```

```{r}
WANDA_NDC$Q4_14_RankParentInfantRelREV <- recode(WANDA_NDC$Q4_14_RankParentInfantRel,
                                             `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_14_RankParentInfantRelSUMNDC <- sum(WANDA_NDC$Q4_14_RankParentInfantRelREV, na.rm = TRUE)
Q4_14_RankParentInfantRelSUMNDC
```

```{r}
WANDA_NDC$Q4_15_RankParentParentRelREV <- recode(WANDA_NDC$Q4_15_RankParentParentRel,
                                             `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_15_RankParentParentRelSUMNDC <- sum(WANDA_NDC$Q4_15_RankParentParentRelREV, na.rm = TRUE)
Q4_15_RankParentParentRelSUMNDC
```


Putting them all into one dataframe

```{r}
summary_df <- data.frame(
  variable = c(
    # WANDA
    "WANDA_Q4_1_RankPrevalenceSUM",
    "WANDA_Q4_2_RankDiagnosisWomenSUM",
    "WANDA_Q4_3_RankDiagnosisPartnersSUM",
    "WANDA_Q4_4_RankBiologicalRiskSUM",
    "WANDA_Q4_5_RankEnvironmentalRiskSUM",
    "WANDA_Q4_6_RankPreviousPregnanciesSUM",
    "WANDA_Q4_7_RankProtectiveFactorsSUM",
    "WANDA_Q4_8_RankInterventionsWomenSUM",
    "WANDA_Q4_9_RankInterventionsPartnersSUM",
    "WANDA_Q4_10_RankHealthOutcomesWomenSUM",
    "WANDA_Q4_11_RankHealthOutcomesPartnersSUM",
    "WANDA_Q4_12_RankHealthOutcomesBabySUM",
    "WANDA_Q4_13_RankSocialEconomicSUM",
    "WANDA_Q4_14_RankParentInfantRelSUM",
    "WANDA_Q4_15_RankParentParentRelSUM",

    # WANDA_NDC
    "WANDA_NDC_Q4_1_RankPrevalenceSUM",
    "WANDA_NDC_Q4_2_RankDiagnosisWomenSUM",
    "WANDA_NDC_Q4_3_RankDiagnosisPartnersSUM",
    "WANDA_NDC_Q4_4_RankBiologicalRiskSUM",
    "WANDA_NDC_Q4_5_RankEnvironmentalRiskSUM",
    "WANDA_NDC_Q4_6_RankPreviousPregnanciesSUM",
    "WANDA_NDC_Q4_7_RankProtectiveFactorsSUM",
    "WANDA_NDC_Q4_8_RankInterventionsWomenSUM",
    "WANDA_NDC_Q4_9_RankInterventionsPartnersSUM",
    "WANDA_NDC_Q4_10_RankHealthOutcomesWomenSUM",
    "WANDA_NDC_Q4_11_RankHealthOutcomesPartnersSUM",
    "WANDA_NDC_Q4_12_RankHealthOutcomesBabySUM",
    "WANDA_NDC_Q4_13_RankSocialEconomicSUM",
    "WANDA_NDC_Q4_14_RankParentInfantRelSUM",
    "WANDA_NDC_Q4_15_RankParentParentRelSUM"
  ),
  value = c(
    # WANDA
    Q4_1_RankPrevalenceSUM,
    Q4_2_RankDiagnosisWomenSUM,
    Q4_3_RankDiagnosisPartnersSUM,
    Q4_4_RankBiologicalRiskSUM,
    Q4_5_RankEnvironmentalRiskSUM,
    Q4_6_RankPreviousPregnanciesSUM,
    Q4_7_RankProtectiveFactorsSUM,
    Q4_8_RankInterventionsWomenSUM,
    Q4_9_RankInterventionsPartnersSUM,
    Q4_10_RankHealthOutcomesWomenSUM,
    Q4_11_RankHealthOutcomesPartnersSUM,
    Q4_12_RankHealthOutcomesBabySUM,
    Q4_13_RankSocialEconomicSUM,
    Q4_14_RankParentInfantRelSUM,
    Q4_15_RankParentParentRelSUM,

    # WANDA_NDC
    Q4_1_RankPrevalenceSUMNDC,
    Q4_2_RankDiagnosisWomenSUMNDC,
    Q4_3_RankDiagnosisPartnersSUMNDC,
    Q4_4_RankBiologicalRiskSUMNDC,
    Q4_5_RankEnvironmentalRiskSUMNDC,
    Q4_6_RankPreviousPregnanciesSUMNDC,
    Q4_7_RankProtectiveFactorsSUMNDC,
    Q4_8_RankInterventionsWomenSUMNDC,
    Q4_9_RankInterventionsPartnersSUMNDC,
    Q4_10_RankHealthOutcomesWomenSUMNDC,
    Q4_11_RankHealthOutcomesPartnersSUMNDC,
    Q4_12_RankHealthOutcomesBabySUMNDC,
    Q4_13_RankSocialEconomicSUMNDC,
    Q4_14_RankParentInfantRelSUMNDC,
    Q4_15_RankParentParentRelSUMNDC
  )
)

print(summary_df)
```

```{r}
summary_df$variable
```
```{r}
summary_df %>% filter(variable == "WANDA_NDC_Q4_1_RankPrevalenceSUM")
```

1) INITIAL BAR CHAR
Making bar chart to see distribution of ranks 

Creating variables for column names and score 
```{r}
VAR_COL   <- "variable" 
SCORE_COL <- "value"
```

Loading packages
```{r}
library(ggplot2)
library(dplyr)
library(stringr)
```

Naming the topics
```{r}
topic_labels <- c(
  WANDA_Q4_1_RankPrevalenceSUM                  = "Prevalence",
  WANDA_Q4_2_RankDiagnosisWomenSUM              = "Diagnosis (for women/birthing people)",
  WANDA_Q4_3_RankDiagnosisPartnersSUM           = "Diagnosis (for partners)",
  WANDA_Q4_4_RankBiologicalRiskSUM              = "Biological risk",
  WANDA_Q4_5_RankEnvironmentalRiskSUM           = "Environmental risk",
  WANDA_Q4_6_RankPreviousPregnanciesSUM         = "Previous pregnancies",
  WANDA_Q4_7_RankProtectiveFactorsSUM           = "Protective factors",
  WANDA_Q4_8_RankInterventionsWomenSUM          = "Interventions (for women/birthing people)",
  WANDA_Q4_9_RankInterventionsPartnersSUM       = "Interventions (for partners)",
  WANDA_Q4_10_RankHealthOutcomesWomenSUM        = "Health outcomes (women/birthing people)",
  WANDA_Q4_11_RankHealthOutcomesPartnersSUM     = "Health outcomes (for partners)",
  WANDA_Q4_12_RankHealthOutcomesBabySUM         = "Health outcomes (baby)",
  WANDA_Q4_13_RankSocialEconomicSUM             = "Social and economic outcomes",
  WANDA_Q4_14_RankParentInfantRelSUM            = "Parent-infant relationship",
  WANDA_Q4_15_RankParentParentRelSUM            = "Parent-parent relationship",
  WANDA_NDC_Q4_1_RankPrevalenceSUM              = "Prevalence",
  WANDA_NDC_Q4_2_RankDiagnosisWomenSUM          = "Diagnosis (for women/birthing people)",
  WANDA_NDC_Q4_3_RankDiagnosisPartnersSUM       = "Diagnosis (for partners)",
  WANDA_NDC_Q4_4_RankBiologicalRiskSUM          = "Biological risk",
  WANDA_NDC_Q4_5_RankEnvironmentalRiskSUM       = "Environmental risk",
  WANDA_NDC_Q4_6_RankPreviousPregnanciesSUM     = "Previous pregnancies",
  WANDA_NDC_Q4_7_RankProtectiveFactorsSUM       = "Protective factors",
  WANDA_NDC_Q4_8_RankInterventionsWomenSUM      = "Interventions (for women/birthing people)",
  WANDA_NDC_Q4_9_RankInterventionsPartnersSUM   = "Interventions (for partners)",
  WANDA_NDC_Q4_10_RankHealthOutcomesWomenSUM    = "Health outcomes (women/birthing people)",
  WANDA_NDC_Q4_11_RankHealthOutcomesPartnersSUM = "Health outcomes (for partners)",
  WANDA_NDC_Q4_12_RankHealthOutcomesBabySUM     = "Health outcomes (baby)",
  WANDA_NDC_Q4_13_RankSocialEconomicSUM         = "Social and economic outcomes",
  WANDA_NDC_Q4_14_RankParentInfantRelSUM        = "Parent-infant relationship",
  WANDA_NDC_Q4_15_RankParentParentRelSUM        = "Parent-parent relationship"
)
```

Wrangling data for plot
```{r}
df <- summary_df %>%
  dplyr::rename(variable = all_of(VAR_COL), score = all_of(SCORE_COL)) %>%
  dplyr::mutate(
    group = if_else(str_detect(variable, "_NDC_"), "NDC subsample (n=212)", "Whole sample (n=709)"),
    topic = topic_labels[variable]
  ) %>%
  filter(!is.na(topic))
```

Order topics by whole-sample priority score (descending - note - ascending so highest ends up at top of flipped axis)
```{r}
topic_order <- df %>%
  filter(group == "Whole sample (n=709)") %>%
  arrange(score) %>%   
  pull(topic)

df <- df %>%
  mutate(topic = factor(topic, levels = topic_order))
```

Annotating the tiers (based on whole-sample rank from table )
```{r}
top_topics <- c(
  "Interventions (for women/birthing people)",
  "Diagnosis (for women/birthing people)",
  "Parent-infant relationship"
)
bottom_topics <- c(
  "Social and economic outcomes",
  "Health outcomes (for partners)"
)
df <- df %>%
  mutate(tier = case_when(
    topic %in% top_topics    ~ ">50%\ntop 5",
    topic %in% bottom_topics ~ "<20%\ntop 5",
    TRUE                     ~ "20–49%\ntop 5"
  ))
```

Setting up the colours
```{r}
group_colours <- c(
  "Whole sample (n=709)"     = "deepskyblue4",
  "NDC subsample (n=212)"    = "indianred4"
)
```

Plot incorporating all the above
```{r}
p <- ggplot(df, aes(x = score, y = topic, fill = group)) +
  geom_col(
    position = position_dodge(width = 0.7),
    width = 0.65,
    alpha = 0.85
  ) +
  scale_fill_manual(values = group_colours, name = NULL) +
  scale_x_continuous(
    name   = "Priority score",
    limits = c(0, NA),
    expand = expansion(mult = c(0, 0.05))
  ) +
  labs(y = NULL) +
  theme_minimal(base_size = 11) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor   = element_blank(),
    panel.grid.major.x = element_line(colour = "grey90"),
    axis.text.y        = element_text(size = 9, colour = "grey30"),
    axis.text.x        = element_text(size = 9, colour = "grey50"),
    axis.title.x       = element_text(size = 10, colour = "grey40", margin = margin(t = 6)),
    legend.position    = "top",
    legend.text        = element_text(size = 10),
    legend.key.size    = unit(0.5, "cm"),
    plot.background    = element_rect(fill = "white", colour = NA),
    panel.background   = element_rect(fill = "white", colour = NA),
    plot.margin        = margin(12, 20, 12, 12)
  )

print(p)
```

Info for the supplementary material 
```{r}
WANDA <- WANDA %>%
  mutate(
    # NO to all three
    group_NoNDC = Q1_4_DiagnosisAutism == "NO. I have never been diagnosed with this" &
                  Q1_3_DiagnosisADHD == "NO. I have never been diagnosed with this" &
                  Q1_6_DiagnosisOtherNeurodev == "NO. I have never been diagnosed with this",

    # Autism Yes
    group_AutismYes = Q1_4_DiagnosisAutism %in% c(
      "YES, I have been diagnosed with this",
      "YES/LIKELY YES. I have never received a diagnosis but this applies to me / I self-identity with this"
    ),

    # Autism Maybe
    group_AutismMaybe = Q1_4_DiagnosisAutism == "MAYBE. I think this may apply to me but I am not sure",

    # ADHD Yes
    group_ADHDYes = Q1_3_DiagnosisADHD %in% c(
      "YES, I have been diagnosed with this",
      "YES/LIKELY YES. I have never received a diagnosis but this applies to me / I self-identity with this"
    ),

    # ADHD Maybe
    group_ADHDMaybe = Q1_3_DiagnosisADHD == "MAYBE. I think this may apply to me but I am not sure",

    # Other Neurodev Yes
    group_OtherNDCYes = Q1_6_DiagnosisOtherNeurodev %in% c(
      "YES, I have been diagnosed with this",
      "YES/LIKELY YES. I have never received a diagnosis but this applies to me / I self-identity with this"
    ),

    # Other Neurodev Maybe
    group_OtherNDCMaybe = Q1_6_DiagnosisOtherNeurodev == "MAYBE. I think this may apply to me but I am not sure"
  )
```

Summarising
```{r}
WANDA %>% dplyr::summarise(across(starts_with("group_"), ~ sum(., na.rm = TRUE)))
```
Now the same but for the actual subgroups in the paper

What unique values 
```{r}
WANDA$Q1_4_DiagnosisAutism <- as.factor(WANDA$Q1_4_DiagnosisAutism)
unique(WANDA$Q1_4_DiagnosisAutism)
```
```{r}
WANDA$Q1_3_DiagnosisADHD <- as.factor(WANDA$Q1_3_DiagnosisADHD)
unique(WANDA$Q1_3_DiagnosisADHD)
```

```{r}
WANDA$Q1_6_DiagnosisOtherNeurodev <- as.factor(WANDA$Q1_6_DiagnosisOtherNeurodev)
unique(WANDA$Q1_6_DiagnosisOtherNeurodev)
```

Creating the groups 
```{r}
WANDA_grouped <- WANDA %>%
  filter(
    Q1_4_DiagnosisAutism      != "Prefer not to answer",
    Q1_3_DiagnosisADHD        != "Prefer not to answer",
    Q1_6_DiagnosisOtherNeurodev != "Prefer not to answer"
  ) %>%
  mutate(
    has_yes = Q1_4_DiagnosisAutism %in% c("YES, I have been diagnosed with this", "YES/LIKELY YES. I have never received a diagnosis but this applies to me / I self-identity with this") |
              Q1_3_DiagnosisADHD %in% c("YES, I have been diagnosed with this", "YES/LIKELY YES. I have never received a diagnosis but this applies to me / I self-identity with this") |
              Q1_6_DiagnosisOtherNeurodev %in% c("YES, I have been diagnosed with this", "YES/LIKELY YES. I have never received a diagnosis but this applies to me / I self-identity with this"),

    has_maybe = Q1_4_DiagnosisAutism == "MAYBE. I think this may apply to me but I am not sure" |
                Q1_3_DiagnosisADHD == "MAYBE. I think this may apply to me but I am not sure" |
                Q1_6_DiagnosisOtherNeurodev == "MAYBE. I think this may apply to me but I am not sure",

    has_no_all = Q1_4_DiagnosisAutism == "NO. I have never been diagnosed with this" &
                 Q1_3_DiagnosisADHD == "NO. I have never been diagnosed with this" &
                 Q1_6_DiagnosisOtherNeurodev == "NO. I have never been diagnosed with this",

    NDC_group = case_when(
      has_yes              ~ "YesNDC",
      has_maybe & !has_yes ~ "MaybeNDC",
      has_no_all           ~ "NoNDC",
      TRUE                 ~ NA_character_  # catches any remaining edge cases
    )
  ) %>%
  filter(!is.na(NDC_group))
```

Checking counts 
```{r}
table(WANDA_grouped$NDC_group)
```


BARCHAT FOR PAPER
(Note - I tried a lot of iterations to see what looks best, but have only kept the code for the version that is in the paper)
```{r}
# ============================================================
# Perinatal Mental Health Research Priorities - Chart v7 updated
# ============================================================

VAR_COL    <- "variable"
SCORE_COL  <- "value"

library(ggplot2)
library(dplyr)
library(stringr)
library(forcats)

# ---- 1. Labels ----
short_labels <- c(
  WANDA_Q4_1_RankPrevalenceSUM                  = "PREVALENCE\n How common are PMHD?",
  WANDA_Q4_2_RankDiagnosisWomenSUM              = "DIAGNOSIS (WOMEN*)\n How can we improve diagnosis of PMHD..?",
  WANDA_Q4_3_RankDiagnosisPartnersSUM           = "DIAGNOSIS (PARTNERS)\n How can we improve diagnosis of PMHD..?",
  WANDA_Q4_4_RankBiologicalRiskSUM              = "BIOLOGICAL RISK\n What biological factors (e.g., genetics, hormones) may put people more at risk?",
  WANDA_Q4_5_RankEnvironmentalRiskSUM           = "ENVIRONMENTAL RISK\n What environmental factors (e.g., poverty) may put people more at risk?",
  WANDA_Q4_6_RankPreviousPregnanciesSUM         = "PREVIOUS PREGNANCIES\n How do previous pregnancies affect someone's perinatal mental health?",
  WANDA_Q4_7_RankProtectiveFactorsSUM           = "PROTECTIVE FACTORS\n What factors may reduce someone's risk for developing PMHD?",
  WANDA_Q4_8_RankInterventionsWomenSUM          = "INTERVENTIONS (WOMEN*)\n What interventions/treatment/support are most effective and appropriate..?",
  WANDA_Q4_9_RankInterventionsPartnersSUM       = "INTERVENTIONS (PARTNERS)\n What interventions/treatment/support are most effective and appropriate..?",
  WANDA_Q4_10_RankHealthOutcomesWomenSUM        = "HEALTH OUTCOMES (WOMEN*)\n What are the long-term physical and mental health outcomes..?",
  WANDA_Q4_11_RankHealthOutcomesPartnersSUM     = "HEALTH OUTCOMES (PARTNERS)\n What are the long-term physical and mental health outcomes..?",
  WANDA_Q4_12_RankHealthOutcomesBabySUM         = "HEALTH OUTCOMES (BABY)\n What are the long-term physical and mental health outcomes of babies?",
  WANDA_Q4_13_RankSocialEconomicSUM             = "SOCIAL AND ECONOMIC OUTCOMES\n What are the long-term social and economic outcomes (e.g., employment, housing)?",
  WANDA_Q4_14_RankParentInfantRelSUM            = "PARENT-INFANT RELATIONSHIP\n Do PMHD affect the relationship between parent and infant?",
  WANDA_Q4_15_RankParentParentRelSUM            = "PARENT-PARENT RELATIONSHIP\n Do PMHD affect the relationship between parents?",
  WANDA_NDC_Q4_1_RankPrevalenceSUM              = "PREVALENCE\n How common are PMHD?",
  WANDA_NDC_Q4_2_RankDiagnosisWomenSUM          = "DIAGNOSIS (WOMEN*)\n How can we improve diagnosis of PMHD..?",
  WANDA_NDC_Q4_3_RankDiagnosisPartnersSUM       = "DIAGNOSIS (PARTNERS)\n How can we improve diagnosis of PMHD..?",
  WANDA_NDC_Q4_4_RankBiologicalRiskSUM          = "BIOLOGICAL RISK\n What biological factors (e.g., genetics, hormones) may put people more at risk?",
  WANDA_NDC_Q4_5_RankEnvironmentalRiskSUM       = "ENVIRONMENTAL RISK\n What environmental factors (e.g., poverty) may put people more at risk?",
  WANDA_NDC_Q4_6_RankPreviousPregnanciesSUM     = "PREVIOUS PREGNANCIES\n How do previous pregnancies affect someone's perinatal mental health?",
  WANDA_NDC_Q4_7_RankProtectiveFactorsSUM       = "PROTECTIVE FACTORS\n What factors may reduce someone's risk for developing PMHD?",
  WANDA_NDC_Q4_8_RankInterventionsWomenSUM      = "INTERVENTIONS (WOMEN*)\n What interventions/treatment/support are most effective and appropriate..?",
  WANDA_NDC_Q4_9_RankInterventionsPartnersSUM   = "INTERVENTIONS (PARTNERS)\n What interventions/treatment/support are most effective and appropriate..?",
  WANDA_NDC_Q4_10_RankHealthOutcomesWomenSUM    = "HEALTH OUTCOMES (WOMEN*)\n What are the long-term physical and mental health outcomes..?",
  WANDA_NDC_Q4_11_RankHealthOutcomesPartnersSUM = "HEALTH OUTCOMES (PARTNERS)\n What are the long-term physical and mental health outcomes..?",
  WANDA_NDC_Q4_12_RankHealthOutcomesBabySUM     = "HEALTH OUTCOMES (BABY)\n What are the long-term physical and mental health outcomes of babies?",
  WANDA_NDC_Q4_13_RankSocialEconomicSUM         = "SOCIAL AND ECONOMIC OUTCOMES\n What are the long-term social and economic outcomes (e.g., employment, housing)?",
  WANDA_NDC_Q4_14_RankParentInfantRelSUM        = "PARENT-INFANT RELATIONSHIP\n Do PMHD affect the relationship between parent and infant?",
  WANDA_NDC_Q4_15_RankParentParentRelSUM        = "PARENT-PARENT RELATIONSHIP\n Do PMHD affect the relationship between parents?"
)

# ---- 2. Mean rank (SD) — labels must match short_labels exactly ----
mean_sd_labels <- tribble(
  ~short_label,                                                                                      
  ~group,                   
  ~mean_sd,
  "PREVALENCE\n How common are PMHD?",                  
  "Whole sample (n=709)",     "3.14 (1.56)",
  "DIAGNOSIS (WOMEN*)\n How can we improve diagnosis of PMHD..?",              
  "Whole sample (n=709)",     "2.26 (1.26)",
  "DIAGNOSIS (PARTNERS)\n How can we improve diagnosis of PMHD..?",          
  "Whole sample (n=709)",     "3.45 (1.26)",
  "BIOLOGICAL RISK\n What biological factors (e.g., genetics, hormones) may put people more at risk?",
  "Whole sample (n=709)",     "3.09 (1.39)",
  "ENVIRONMENTAL RISK\n What environmental factors (e.g., poverty) may put people more at risk?",   
  "Whole sample (n=709)",     "3.48 (1.41)",
  "PREVIOUS PREGNANCIES\n How do previous pregnancies affect someone's perinatal mental health?",   
  "Whole sample (n=709)",     "2.82 (1.40)",
  "PROTECTIVE FACTORS\n What factors may reduce someone's risk for developing PMHD?",         
  "Whole sample (n=709)",     "2.98 (1.44)",
  "INTERVENTIONS (WOMEN*)\n What interventions/treatment/support are most effective and appropriate..?",
  "Whole sample (n=709)",     "2.38 (1.26)",
  "INTERVENTIONS (PARTNERS)\n What interventions/treatment/support are most effective and appropriate..?",
  "Whole sample (n=709)",   "3.59 (1.19)",
  "HEALTH OUTCOMES (WOMEN*)\n What are the long-term physical and mental health outcomes..?",               
  "Whole sample (n=709)",     "3.02 (1.23)",
  "HEALTH OUTCOMES (PARTNERS)\n What are the long-term physical and mental health outcomes..?",           
  "Whole sample (n=709)",     "4.12 (1.10)",
  "HEALTH OUTCOMES (BABY)\n What are the long-term physical and mental health outcomes of babies?",       
  "Whole sample (n=709)",     "2.95 (1.34)",
  "SOCIAL AND ECONOMIC OUTCOMES\n What are the long-term social and economic outcomes (e.g., employment, housing)?",
  "Whole sample (n=709)", "4.05 (1.16)",
  "PARENT-INFANT RELATIONSHIP\n Do PMHD affect the relationship between parent and infant?",          
  "Whole sample (n=709)",     "3.08 (1.34)",
  "PARENT-PARENT RELATIONSHIP\n Do PMHD affect the relationship between parents?",                   
  "Whole sample (n=709)",     "4.06 (1.20)",
  "PREVALENCE\n How common are PMHD?",                                                               
  "NDC subsample (n=212)",    "3.00 (1.57)",
  "DIAGNOSIS (WOMEN*)\n How can we improve diagnosis of PMHD..?",                                     
  "NDC subsample (n=212)",    "2.24 (1.31)",
  "DIAGNOSIS (PARTNERS)\n How can we improve diagnosis of PMHD..?",                           
  "NDC subsample (n=212)",    "3.29 (1.32)",
  "BIOLOGICAL RISK\n What biological factors (e.g., genetics, hormones) may put people more at risk?",  
  "NDC subsample (n=212)",    "2.98 (1.42)",
  "ENVIRONMENTAL RISK\n What environmental factors (e.g., poverty) may put people more at risk?",   
  "NDC subsample (n=212)",    "3.57 (1.38)",
  "PREVIOUS PREGNANCIES\n How do previous pregnancies affect someone's perinatal mental health?",         
  "NDC subsample (n=212)",    "2.62 (1.35)",
  "PROTECTIVE FACTORS\n What factors may reduce someone's risk for developing PMHD?",               
  "NDC subsample (n=212)",    "3.06 (1.36)",
  "INTERVENTIONS (WOMEN*)\n What interventions/treatment/support are most effective and appropriate..?",
  "NDC subsample (n=212)",    "2.44 (1.30)",
  "INTERVENTIONS (PARTNERS)\n What interventions/treatment/support are most effective and appropriate..?",
  "NDC subsample (n=212)",  "3.33 (1.21)",
  "HEALTH OUTCOMES (WOMEN*)\n What are the long-term physical and mental health outcomes..?",                 
  "NDC subsample (n=212)",    "3.15 (1.33)",
  "HEALTH OUTCOMES (PARTNERS)\n What are the long-term physical and mental health outcomes..?",               
  "NDC subsample (n=212)",    "3.78 (1.09)",
  "HEALTH OUTCOMES (BABY)\n What are the long-term physical and mental health outcomes of babies?",          
  "NDC subsample (n=212)",    "3.27 (1.35)",
  "SOCIAL AND ECONOMIC OUTCOMES\n What are the long-term social and economic outcomes (e.g., employment, housing)?", 
  "NDC subsample (n=212)", "4.00 (1.20)",
  "PARENT-INFANT RELATIONSHIP\n Do PMHD affect the relationship between parent and infant?",          
  "NDC subsample (n=212)",    "3.14 (1.35)",
  "PARENT-PARENT RELATIONSHIP\n Do PMHD affect the relationship between parents?",                
  "NDC subsample (n=212)",    "3.85 (1.25)"
)

# ---- 3. Tier membership ----
top_keys <- c(
  "WANDA_Q4_8_RankInterventionsWomenSUM",
  "WANDA_Q4_2_RankDiagnosisWomenSUM",
  "WANDA_Q4_14_RankParentInfantRelSUM"
)
bottom_keys <- c(
  "WANDA_Q4_13_RankSocialEconomicSUM",
  "WANDA_Q4_11_RankHealthOutcomesPartnersSUM"
)

# ---- 4. Wrangle ----
df <- summary_df %>%
  dplyr::rename(variable = all_of(VAR_COL), score = all_of(SCORE_COL)) %>%
  mutate(
    group       = if_else(str_detect(variable, "_NDC_"), "NDC subsample (n=212)", "Whole sample (n=709)"),
    short_label = short_labels[variable],
    tier = case_when(
      variable %in% top_keys | str_replace(variable, "WANDA_NDC_Q4_", "WANDA_Q4_") %in% top_keys       ~ ">50% ranked in top 5",
      variable %in% bottom_keys | str_replace(variable, "WANDA_NDC_Q4_", "WANDA_Q4_") %in% bottom_keys ~ "<20% ranked in top 5",
      TRUE ~ "20-49% ranked in top 5"
    ),
    tier = factor(tier, levels = c(
      ">50% ranked in top 5",
      "20-49% ranked in top 5",
      "<20% ranked in top 5"
    ))
  ) %>%
  filter(!is.na(short_label)) %>%
  left_join(mean_sd_labels, by = c("short_label", "group"))

# ---- 5. Topic order — must match short_labels exactly ----
topic_order <- c(
  "INTERVENTIONS (WOMEN*)\n What interventions/treatment/support are most effective and appropriate..?",
  "DIAGNOSIS (WOMEN*)\n How can we improve diagnosis of PMHD..?",
  "PARENT-INFANT RELATIONSHIP\n Do PMHD affect the relationship between parent and infant?",
  "HEALTH OUTCOMES (WOMEN*)\n What are the long-term physical and mental health outcomes..?",
  "HEALTH OUTCOMES (BABY)\n What are the long-term physical and mental health outcomes of babies?",
  "PROTECTIVE FACTORS\n What factors may reduce someone's risk for developing PMHD?",
  "PREVIOUS PREGNANCIES\n How do previous pregnancies affect someone's perinatal mental health?",
  "PREVALENCE\n How common are PMHD?",
  "ENVIRONMENTAL RISK\n What environmental factors (e.g., poverty) may put people more at risk?",
  "BIOLOGICAL RISK\n What biological factors (e.g., genetics, hormones) may put people more at risk?",
  "DIAGNOSIS (PARTNERS)\n How can we improve diagnosis of PMHD..?",
  "PARENT-PARENT RELATIONSHIP\n Do PMHD affect the relationship between parents?",
  "INTERVENTIONS (PARTNERS)\n What interventions/treatment/support are most effective and appropriate..?",
  "SOCIAL AND ECONOMIC OUTCOMES\n What are the long-term social and economic outcomes (e.g., employment, housing)?",
  "HEALTH OUTCOMES (PARTNERS)\n What are the long-term physical and mental health outcomes..?"
)

df <- df %>%
  mutate(
    short_label = factor(short_label, levels = rev(topic_order)),
    tier = fct_relevel(tier, ">50% ranked in top 5", "20-49% ranked in top 5", "<20% ranked in top 5")
  )

# ---- 6. Colours ----
group_colours <- c(
  "Whole sample (n=709)"  = "#5340B7",
  "NDC subsample (n=212)" = "#1D9E75"
)

# ---- 7. Plot ----
p_barchart7 <- ggplot(df, aes(x = score, y = short_label, fill = group)) +
  geom_col(
    position = position_dodge(width = 0.85),
    width    = 0.82,
    alpha    = 0.85
  ) +
  geom_text(
    aes(label = mean_sd, group = group),
    position = position_dodge(width = 0.85),
    hjust    = -0.1,
    size     = 7,
    colour   = "black"
  ) +
  facet_grid(
    tier ~ .,
    scales   = "free_y",
    space    = "free_y",
    labeller = label_wrap_gen(width = 10)
  ) +
  scale_fill_manual(values = group_colours, name = NULL) +
  scale_x_continuous(
    name   = "Priority score",
    limits = c(0, NA),
    expand = expansion(mult = c(0, 0.18))
  ) +
  coord_cartesian(clip = "off") + 
  labs(y = NULL) +
  theme_minimal(base_size = 22) +
  theme(
    panel.grid.major.y  = element_blank(),
    panel.grid.minor    = element_blank(),
    panel.grid.major.x  = element_line(colour = "white"),
    axis.text.y         = element_text(size = 19, colour = "black",
                                       lineheight = 1.1),
    axis.text.x         = element_text(size =20, colour = "black"),
    axis.title.x        = element_text(size = 20, colour = "black", margin = margin(t = 6)),
    legend.position     = "bottom",
    legend.text         = element_text(size = 21),
    legend.key.size     = unit(0.55, "cm"),
    strip.background  = element_rect(fill = NA, colour = NA),
    strip.text.y      = element_text(size = 20, face = "bold", colour = "black",
                                 angle = 0, hjust = 0),
    panel.border      = element_rect(fill = NA, colour = "grey80", linewidth = 0.4),
    panel.spacing       = unit(0.2, "lines"),
    plot.background     = element_rect(fill = "white", colour = NA),
    panel.background    = element_rect(fill = "grey95", colour = NA),
    plot.margin         = margin(12, 20, 12, 12),
    plot.caption = element_text(size = 15, colour = "black", margin = margin(t = 8, l = 100))
  )

print(p_barchart7)

# ---- 8. Save ----
ggsave(
  "perinatal_priorities_chart_v7_updated.png",
  plot   = p_barchart7,
  width  = 20,
  height = 22,
  dpi    = 300,
  bg     = "white"
)

message("Saved as perinatal_priorities_chart_v7_updated.png")
```
Similar for heatmap (only kept the code for the plot that ended up making into the publication)

```{r}

# ============================================================
# Perinatal Mental Health Research Priorities - Heatmap
# Rows = topics, Columns = neurotype groups
# Fill = normalised priority score (per participant)
# ============================================================

library(ggplot2)
library(dplyr)
library(tidyr)

# ---- 1. Data ----
# Raw priority scores and group Ns
n_per_group <- c(
  "No NDC"          = 398,
  "Autism Yes"      = 86,
  "Autism Maybe"    = 77,
  "ADHD Yes"        = 104,
  "ADHD Maybe"      = 89,
  "Other NDC Yes"   = 82,
  "Other NDC Maybe" = 23
)

heatmap_df <- tribble(
  ~topic,                                    ~`No NDC`, ~`Autism Yes`, ~`Autism Maybe`, ~`ADHD Yes`, ~`ADHD Maybe`, ~`Other NDC Yes`, ~`Other NDC Maybe`,
  "Interventions (women*)",   1033,       255,           183,             242,         253,           219,              49,
  "Diagnosis (women*)",        886,       191,           155,             241,         159,           167,              47,
  "Parent-infant relationship",               648,       127,           102,             147,         138,           150,              26,
  "Health outcomes (women*)",  514,        98,            95,             115,         111,            86,              42,
  "Health outcomes (baby)",                   496,        94,            91,             106,          95,            83,              31,
  "Protective factors",                       410,        71,           115,             114,         122,            91,              32,
  "Previous pregnancies",                     436,        88,            73,             124,          84,            91,              32,
  "Prevalence",                               263,        64,            63,             115,          62,            80,              24,
  "Environmental risk",                       275,        48,            93,              77,          53,            45,               7,
  "Biological risk",                          250,        57,            51,              72,          68,            40,               6,
  "Diagnosis (partners)",                     198,        66,            46,              55,          54,            53,              25,
  "Parent-parent relationship",               211,        41,            38,              56,          46,            59,               6,
  "Interventions (partners)",                 210,        54,            23,              34,          46,            32,               9,
  "Social & economic outcomes",               105,        20,            22,              52,          29,            27,               2,
  "Health outcomes (partners)",                31,        16,             5,              10,          15,             7,               7
)

# ---- 2. Normalise scores per participant within each group ----
# This makes groups comparable despite different sample sizes
heatmap_long <- heatmap_df %>%
  pivot_longer(-topic, names_to = "group", values_to = "priority_score") %>%
  mutate(
    n     = n_per_group[group],
    score_per_person = priority_score / n,
    # Order topics by No NDC priority score (descending) to match main figure
    topic = factor(topic, levels = rev(c(
      "Interventions (women*)",
      "Diagnosis (women*)",
      "Parent-infant relationship",
      "Health outcomes (women*)",
      "Health outcomes (baby)",
      "Protective factors",
      "Previous pregnancies",
      "Prevalence",
      "Environmental risk",
      "Biological risk",
      "Diagnosis (partners)",
      "Parent-parent relationship",
      "Interventions (partners)",
      "Social & economic outcomes",
      "Health outcomes (partners)"
    ))),
    # Order groups logically
    group = factor(group, levels = c(
      "No NDC",
      "Autism Yes", "Autism Maybe",
      "ADHD Yes",   "ADHD Maybe",
      "Other NDC Yes", "Other NDC Maybe"
    ))
  )

# ---- 3. Plot ----
p_nolabels <- ggplot(heatmap_long, aes(x = group, y = topic, fill = score_per_person)) +
  geom_tile(colour = "white", linewidth = 0.5) +
  # show raw score in each cell
  geom_text(aes(label = priority_score), size = 7, colour = "black") +
    scale_fill_gradient(
    low  = "#EEF4FB",
    high = "orchid3",
    name = "Priority score\n(per participant)",
    guide = "none"
  ) +
  scale_x_discrete(position = "bottom") +
  labs(x = NULL, y = NULL,
       caption = "Bar chart: Priority scores - higher scores reflect a higher level of prioritisation. Ranking scores were reverse scored and then a sum was calculated across all participants for each individual priority. \nHeatmap: Cell values show raw priority scores. Colour intensity reflects score normalised by group size. WOMEN* = women and birthing people, PMHD = perinatal mental health difficulties, NDC = neurodevelopmental conditions. \nNDC subsample includes Yes or Likely Yes answers to any of the questions regarding a (self-)diagnosis of autism, ADHD, or other NDCs like dyslexia or dyspraxia; it does not include participants who answered Maybe.") +
  theme_minimal(base_size = 19) +
  theme(axis.text.x = element_text(
  colour = c("black", "#1D9E75", "goldenrod3", 
             "#1D9E75", "goldenrod3", "#1D9E75", "goldenrod3"), angle=-20, size=22, hjust=0),
    axis.text.y       = element_blank(),
    panel.grid        = element_blank(),
    legend.position   = "right",
    legend.title      = element_text(size = 19),
    legend.text       = element_text(size = 19),
    plot.caption      = element_text(size = 19, colour = "black", margin = margin(t = 8), hjust=0),
    plot.background   = element_rect(fill = "white", colour = NA),
    panel.background  = element_rect(fill = "white", colour = NA),
    plot.margin       = margin(12, 12, 12, 12)
  )

print(p_nolabels)

# ---- 4. Save ----
ggsave(
  "perinatal_priorities_heatmap.png",
  plot   = p_nolabels,
  width  = 11,
  height = 8,
  dpi    = 300,
  bg     = "white"
)

message("Saved as perinatal_priorities_heatmap.png")
```
Checking class of figures
```{r}
class(p_nolabels)
class(p_barchart7)
```


Combining both figures into one
```{r}
library(patchwork)
combined <- p_nolabels + p_barchart7 +
  plot_layout(widths = c(2, 1.5), guides = "collect") &
  theme(legend.position = "bottom")

ggsave("combined_figure.pdf", plot = combined, width = 28, height = 18, dpi = 300, bg = "white")
```





















