---
title: "WANDA Priorities"
output: pdf_document
date: "2025-09-10"
---

This is an RMarkdown document summarising the quantitative data analysis for the priorities paper.

# SETTING UP ENVIRONMENT
Loading the packages I use most. Suppressing messages from appearing in RMarkdown doc, so they do not take up space.
```{r results="hide", warning=FALSE, comment=FALSE, message=FALSE}
library(ggplot2)
library(janitor)
library(dplyr)
library(writexl)
library(psych)
library(Hmisc)
library(plyr)
library(ggExtra)
library(doBy)
library(grid)
```

Turn off scientific notation
```{r}
options(scipen=999) 
```

Set theme for future plots
```{r}
theme_set(
        theme_minimal((base_size = 16)) +
                theme(legend.position = "right"))
```

Preparing the data: This sets up the R environment and ensurs readr is installed/loaded and configuring knitr to display code in the output.
```{r setup, include=FALSE}
options(repos = c(CRAN = "https://cran.r-project.org"))
if (!requireNamespace("readr", quietly = TRUE)) {
  install.packages("readr")
}
library(readr)

knitr::opts_chunk$set(echo = TRUE)
```

Check R version
```{r}
R.version
```

Loading dataset
```{r}
WANDA <- read.csv("MERGED_MOTHERS_USE_2_TOSHARE_CLEANED_300625.csv", header=TRUE, na.string=c("","NA", " ", "not known", "-997", "-998","-999", "-996"))
```

```{r}
str(WANDA)
```

DEMOGRAPHICS 

```{r}
psych::describe(WANDA$Q1_AgeYears)
```

Frequencies for diagnosis autism 
```{r}
table(WANDA$Q1_4_DiagnosisAutism)
```

Manual checks
How many yes autism
```{r}
32+54
```

Percentage yes autism
```{r}
8600/709
```

How many yes and maybes autism
```{r}
54+32+77
```

Percentage autism yes and maybe
```{r}
(163*100)/709
```

Frequencies for diagnosis ADHD 
```{r}
table(WANDA$Q1_3_DiagnosisADHD)
```

Manual checks
How many yeses
```{r}
31+73
```

Percentage yeses
```{r}
10400/709
```

How many including maybes
```{r}
104+89
```

Percentage including maybes
```{r}
19300/709
```

Frequencies for diagnosis other NDCs
```{r}
table(WANDA$Q1_6_DiagnosisOtherNeurodev)
```

Manual checks
How many yeses
```{r}
67+15
```

Percentage yeses
```{r}
8200/709
```

Numbers including maybe
```{r}
82+23
```

Percentage including maybe
```{r}
10500/709
```



Frequencies for diagnosis depression 

```{r}
table(WANDA$Q1_1_DiagnosisDepression)
```

Manual checks
Frequency for depression yes
```{r}
70+302
```

Percentages for depression
```{r}
37200/709
```

Frequencies for depresssion yes and maybe
```{r}
372+59
```

Percentages
```{r}
43100/709
```

Frequencies for diagnosis anxiety
```{r}
table(WANDA$Q1_2_DiagnosisAnxiety)
```

Manual checks
Frequency yes anxiety
```{r}
315+109
```

Percentages
```{r}
42400/709
```

Plus maybes
```{r}
424+83
```

Percentages
```{r}
50700/709
```

Frequencies for diagnosis other mental health conditions
```{r}
table(WANDA$Q1_5_DiagnosisOtherMentalHealth)
```
Frequency yes
```{r}
108+44
```

Percentage yes
```{r}
15200/709
```

Frequency plus maybes
```{r}
152+38
```

Percentages
```{r}
19000/709
```


Other demographics
```{r}
tabyl(WANDA$Q2_GenderIdentity)
```
```{r}
tabyl(WANDA$Q3_SexualOrientation)
```
```{r}
tabyl(WANDA$Q4_RaceEthnicity)
```

Manual check
```{r}
.8222+.0013+.0028+.0789+.0028
```

Education
```{r}
tabyl(WANDA$Q5_Education)
```

Manual check
```{r}
.4542+.3681
```

Relationship status
```{r}
tabyl(WANDA$Q4_RelationshipStatus)
```

Manual check
```{r}
.2426+.7151
```

Pregnancy status
```{r}
tabyl(WANDA$Q3_YouPregnant)
```

Manual check
```{r}
.1368+.0522
```

Pregnancy during covid
```{r}
tabyl(WANDA$Q5_PregnancyDuringCovid)
```

Manual check
```{r}
.1594+.1608
```

CREATING SUBSETS OF DATAFRAMES 

NEURODIVERGENT SAMPLE 
Subset: any variable where the answwer is Yes / Likely Yes, and none are "Prefer not to answer"
```{r}
WANDA_NDC <- subset(
  WANDA,
  (Q1_4_DiagnosisAutism %in% c(
     "YES, I have been diagnosed with this",
     "YES/LIKELY YES. I have never received a diagnosis but this applies to me / I self-identity with this"
   ) |
   Q1_3_DiagnosisADHD %in% c(
     "YES, I have been diagnosed with this",
     "YES/LIKELY YES. I have never received a diagnosis but this applies to me / I self-identity with this"
   ) |
   Q1_6_DiagnosisOtherNeurodev %in% c(
     "YES, I have been diagnosed with this",
     "YES/LIKELY YES. I have never received a diagnosis but this applies to me / I self-identity with this"
   ))
)
```

Check structure
```{r}
str(WANDA_NDC)
```

How many people ranked each in top 5 and mean rank
```{r}
tabyl(WANDA$Q4_1_RankPrevalence)
```

```{r}
709-523
```

```{r}
18600/709
```

```{r}
psych::describe(WANDA$Q4_1_RankPrevalence)
```



```{r}
tabyl(WANDA$Q4_8_RankInterventionsWomen)
```

```{r}
709-197
```

```{r}
51200/709
```

```{r}
psych::describe(WANDA$Q4_8_RankInterventionsWomen)
```



```{r}
tabyl(WANDA$Q4_2_RankDiagnosisWomen)
```

```{r}
709-298
```

```{r}
41100/709
```

```{r}
psych::describe(WANDA$Q4_2_RankDiagnosisWomen)
```



```{r}
tabyl(WANDA$Q4_15_RankParentParentRel)
```

```{r}
709-513
```

```{r}
19600/709
```

```{r}
psych::describe(WANDA$Q4_15_RankParentParentRel)
```



```{r}
tabyl(WANDA$Q4_14_RankParentInfantRel)
```

```{r}
709-322
```

```{r}
38700/709
```

```{r}
psych::describe(WANDA$Q4_14_RankParentInfantRel)
```



```{r}
tabyl(WANDA$Q4_10_RankHealthOutcomesWomen)
```

```{r}
709-415
```

```{r}
29400/709
```

```{r}
psych::describe(WANDA$Q4_10_RankHealthOutcomesWomen)
```



```{r}
tabyl(WANDA$Q4_12_RankHealthOutcomesBaby)
```

```{r}
709-436
```

```{r}
27300/709
```

```{r}
psych::describe(WANDA$Q4_12_RankHealthOutcomesBaby)
```



```{r}
tabyl(WANDA$Q4_7_RankProtectiveFactors)
```

```{r}
709-446
```

```{r}
26300/709
```

```{r}
psych::describe(WANDA$Q4_7_RankProtectiveFactors)
```



```{r}
tabyl(WANDA$Q4_6_RankPreviousPregnancies)
```

```{r}
709-476
```

```{r}
23300/709
```

```{r}
psych::describe(WANDA$Q4_6_RankPreviousPregnancies)
```



```{r}
tabyl(WANDA$Q4_5_RankEnvironmentalRisk)
```

```{r}
709-517
```

```{r}
19200/709
```

```{r}
psych::describe(WANDA$Q4_5_RankEnvironmentalRisk)
```



```{r}
tabyl(WANDA$Q4_4_RankBiologicalRisk)
```

```{r}
709-555
```

```{r}
15400/709
```

```{r}
psych::describe(WANDA$Q4_4_RankBiologicalRisk)
```



```{r}
tabyl(WANDA$Q4_3_RankDiagnosisPartners)
```

```{r}
709-554
```

```{r}
15500/709
```

```{r}
psych::describe(WANDA$Q4_3_RankDiagnosisPartners)
```



```{r}
tabyl(WANDA$Q4_9_RankInterventionsPartners)
```

```{r}
709-560
```

```{r}
14900/709
```

```{r}
psych::describe(WANDA$Q4_9_RankInterventionsPartners)
```



```{r}
tabyl(WANDA$Q4_13_RankSocialEconomic)
```

```{r}
709-601
```

```{r}
10800/709
```

```{r}
psych::describe(WANDA$Q4_13_RankSocialEconomic)
```



```{r}
tabyl(WANDA$Q4_11_RankHealthOutcomesPartners)
```

```{r}
709-677
```

```{r}
3200/709
```

```{r}
psych::describe(WANDA$Q4_11_RankHealthOutcomesPartners)
```



Repeating above for NDC subsample 
```{r}
tabyl(WANDA_NDC$Q4_1_RankPrevalence)
```

```{r}
212-146
```

```{r}
6600/212
```

```{r}
psych::describe(WANDA_NDC$Q4_1_RankPrevalence)
```



```{r}
tabyl(WANDA_NDC$Q4_8_RankInterventionsWomen)
```

```{r}
212-55
```

```{r}
15700/212
```

```{r}
psych::describe(WANDA_NDC$Q4_8_RankInterventionsWomen)
```


```{r}
tabyl(WANDA_NDC$Q4_2_RankDiagnosisWomen)
```

```{r}
212-89
```

```{r}
12300/212
```

```{r}
psych::describe(WANDA_NDC$Q4_2_RankDiagnosisWomen)
```



```{r}
tabyl(WANDA_NDC$Q4_15_RankParentParentRel)
```

```{r}
212-152
```

```{r}
6000/212
```

```{r}
psych::describe(WANDA_NDC$Q4_15_RankParentParentRel)
```



```{r}
tabyl(WANDA_NDC$Q4_14_RankParentInfantRel)
```

```{r}
212-94
```

```{r}
11800/212
```

```{r}
psych::describe(WANDA_NDC$Q4_14_RankParentInfantRel)
```



```{r}
tabyl(WANDA_NDC$Q4_10_RankHealthOutcomesWomen)
```

```{r}
212-134
```

```{r}
7800/212
```

```{r}
psych::describe(WANDA_NDC$Q4_10_RankHealthOutcomesWomen)
```


```{r}
tabyl(WANDA_NDC$Q4_12_RankHealthOutcomesBaby)
```

```{r}
212-131
```

```{r}
8100/212
```

```{r}
psych::describe(WANDA_NDC$Q4_12_RankHealthOutcomesBaby)
```



```{r}
tabyl(WANDA_NDC$Q4_7_RankProtectiveFactors)
```

```{r}
212-132
```

```{r}
8000/212
```

```{r}
psych::describe(WANDA_NDC$Q4_7_RankProtectiveFactors)
```



```{r}
tabyl(WANDA_NDC$Q4_6_RankPreviousPregnancies)
```

```{r}
212-149
```

```{r}
6300/212
```

```{r}
psych::describe(WANDA_NDC$Q4_6_RankPreviousPregnancies)
```



```{r}
tabyl(WANDA_NDC$Q4_5_RankEnvironmentalRisk)
```

```{r}
212-159
```

```{r}
5300/212
```

```{r}
psych::describe(WANDA_NDC$Q4_5_RankEnvironmentalRisk)
```



```{r}
tabyl(WANDA_NDC$Q4_4_RankBiologicalRisk)
```

```{r}
212-168
```

```{r}
4400/212
```

```{r}
psych::describe(WANDA_NDC$Q4_4_RankBiologicalRisk)
```



```{r}
tabyl(WANDA_NDC$Q4_3_RankDiagnosisPartners)
```

```{r}
212-160
```

```{r}
5200/212
```

```{r}
psych::describe(WANDA_NDC$Q4_3_RankDiagnosisPartners)
```



```{r}
tabyl(WANDA_NDC$Q4_9_RankInterventionsPartners)
```

```{r}
212-172
```

```{r}
4000/212
```

```{r}
psych::describe(WANDA_NDC$Q4_9_RankInterventionsPartners)
```

```{r}
tabyl(WANDA_NDC$Q4_13_RankSocialEconomic)
```

```{r}
212-176
```

```{r}
3600/212
```

```{r}
psych::describe(WANDA_NDC$Q4_13_RankSocialEconomic)
```

```{r}
tabyl(WANDA_NDC$Q4_11_RankHealthOutcomesPartners)
```

```{r}
212-203
```

```{r}
900/212
```

```{r}
psych::describe(WANDA_NDC$Q4_11_RankHealthOutcomesPartners)
```


Calculating priority scores

```{r}
str(WANDA$Q4_1_RankPrevalence)
```

```{r}
WANDA$Q4_1_RankPrevalenceREV <- recode(WANDA$Q4_1_RankPrevalence,
                                       `1` = 5,
                                       `2` = 4,
                                       `3` = 3,
                                       `4` = 2,
                                       `5` = 1)
```

```{r}
Q4_1_RankPrevalenceSUM <- sum(WANDA$Q4_1_RankPrevalenceREV, na.rm = TRUE)
Q4_1_RankPrevalenceSUM
```

Now listing all variables that contain "rank"
```{r}
vars <- grep("Rank", names(WANDA), value = TRUE)
print(vars)
```

Running the code for all of them to reverse score
```{r}
WANDA$Q4_2_RankDiagnosisWomenREV <- recode(WANDA$Q4_2_RankDiagnosisWomen,
                                           `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_2_RankDiagnosisWomenSUM <- sum(WANDA$Q4_2_RankDiagnosisWomenREV, na.rm = TRUE)
Q4_2_RankDiagnosisWomenSUM
```


```{r}
WANDA$Q4_3_RankDiagnosisPartnersREV <- recode(WANDA$Q4_3_RankDiagnosisPartners,
                                              `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_3_RankDiagnosisPartnersSUM <- sum(WANDA$Q4_3_RankDiagnosisPartnersREV, na.rm = TRUE)
Q4_3_RankDiagnosisPartnersSUM
```

```{r}
WANDA$Q4_4_RankBiologicalRiskREV <- recode(WANDA$Q4_4_RankBiologicalRisk,
                                           `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_4_RankBiologicalRiskSUM <- sum(WANDA$Q4_4_RankBiologicalRiskREV, na.rm = TRUE)
Q4_4_RankBiologicalRiskSUM
```

```{r}
WANDA$Q4_5_RankEnvironmentalRiskREV <- recode(WANDA$Q4_5_RankEnvironmentalRisk,
                                              `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_5_RankEnvironmentalRiskSUM <- sum(WANDA$Q4_5_RankEnvironmentalRiskREV, na.rm = TRUE)
Q4_5_RankEnvironmentalRiskSUM
```

```{r}
WANDA$Q4_6_RankPreviousPregnanciesREV <- recode(WANDA$Q4_6_RankPreviousPregnancies,
                                                `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_6_RankPreviousPregnanciesSUM <- sum(WANDA$Q4_6_RankPreviousPregnanciesREV, na.rm = TRUE)
Q4_6_RankPreviousPregnanciesSUM
```

```{r}
WANDA$Q4_7_RankProtectiveFactorsREV <- recode(WANDA$Q4_7_RankProtectiveFactors,
                                              `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_7_RankProtectiveFactorsSUM <- sum(WANDA$Q4_7_RankProtectiveFactorsREV, na.rm = TRUE)
Q4_7_RankProtectiveFactorsSUM
```

```{r}
WANDA$Q4_8_RankInterventionsWomenREV <- recode(WANDA$Q4_8_RankInterventionsWomen,
                                               `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_8_RankInterventionsWomenSUM <- sum(WANDA$Q4_8_RankInterventionsWomenREV, na.rm = TRUE)
Q4_8_RankInterventionsWomenSUM
```

```{r}
WANDA$Q4_9_RankInterventionsPartnersREV <- recode(WANDA$Q4_9_RankInterventionsPartners,
                                                  `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_9_RankInterventionsPartnersSUM <- sum(WANDA$Q4_9_RankInterventionsPartnersREV, na.rm = TRUE)
Q4_9_RankInterventionsPartnersSUM
```

```{r}
WANDA$Q4_10_RankHealthOutcomesWomenREV <- recode(WANDA$Q4_10_RankHealthOutcomesWomen,
                                                 `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_10_RankHealthOutcomesWomenSUM <- sum(WANDA$Q4_10_RankHealthOutcomesWomenREV, na.rm = TRUE)
Q4_10_RankHealthOutcomesWomenSUM
```

```{r}
WANDA$Q4_11_RankHealthOutcomesPartnersREV <- recode(WANDA$Q4_11_RankHealthOutcomesPartners,
                                                    `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_11_RankHealthOutcomesPartnersSUM <- sum(WANDA$Q4_11_RankHealthOutcomesPartnersREV, na.rm = TRUE)
Q4_11_RankHealthOutcomesPartnersSUM
```

```{r}
WANDA$Q4_12_RankHealthOutcomesBabyREV <- recode(WANDA$Q4_12_RankHealthOutcomesBaby,
                                                `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_12_RankHealthOutcomesBabySUM <- sum(WANDA$Q4_12_RankHealthOutcomesBabyREV, na.rm = TRUE)
Q4_12_RankHealthOutcomesBabySUM
```

```{r}
WANDA$Q4_13_RankSocialEconomicREV <- recode(WANDA$Q4_13_RankSocialEconomic,
                                            `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_13_RankSocialEconomicSUM <- sum(WANDA$Q4_13_RankSocialEconomicREV, na.rm = TRUE)
Q4_13_RankSocialEconomicSUM
```

```{r}
WANDA$Q4_14_RankParentInfantRelREV <- recode(WANDA$Q4_14_RankParentInfantRel,
                                             `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_14_RankParentInfantRelSUM <- sum(WANDA$Q4_14_RankParentInfantRelREV, na.rm = TRUE)
Q4_14_RankParentInfantRelSUM
```

```{r}
WANDA$Q4_15_RankParentParentRelREV <- recode(WANDA$Q4_15_RankParentParentRel,
                                             `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_15_RankParentParentRelSUM <- sum(WANDA$Q4_15_RankParentParentRelREV, na.rm = TRUE)
Q4_15_RankParentParentRelSUM
```


Now same for the NDC subsample

```{r}
WANDA_NDC$Q4_1_RankPrevalenceREV <- recode(WANDA_NDC$Q4_1_RankPrevalence,
                                       `1` = 5,
                                       `2` = 4,
                                       `3` = 3,
                                       `4` = 2,
                                       `5` = 1)
NDCQ4_1_RankPrevalenceSUM <- sum(WANDA_NDC$Q4_1_RankPrevalenceREV, na.rm = TRUE)
NDCQ4_1_RankPrevalenceSUM
```

```{r}
WANDA_NDC$Q4_2_RankDiagnosisWomenREV <- recode(WANDA_NDC$Q4_2_RankDiagnosisWomen,
                                           `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_2_RankDiagnosisWomenSUMNDC <- sum(WANDA_NDC$Q4_2_RankDiagnosisWomenREV, na.rm = TRUE)
Q4_2_RankDiagnosisWomenSUMNDC
```

```{r}
WANDA_NDC$Q4_3_RankDiagnosisPartnersREV <- recode(WANDA_NDC$Q4_3_RankDiagnosisPartners,
                                              `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_3_RankDiagnosisPartnersSUMNDC <- sum(WANDA_NDC$Q4_3_RankDiagnosisPartnersREV, na.rm = TRUE)
Q4_3_RankDiagnosisPartnersSUMNDC
```

```{r}
WANDA_NDC$Q4_4_RankBiologicalRiskREV <- recode(WANDA_NDC$Q4_4_RankBiologicalRisk,
                                           `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_4_RankBiologicalRiskSUMNDC <- sum(WANDA_NDC$Q4_4_RankBiologicalRiskREV, na.rm = TRUE)
Q4_4_RankBiologicalRiskSUMNDC
```

```{r}
WANDA_NDC$Q4_5_RankEnvironmentalRiskREV <- recode(WANDA_NDC$Q4_5_RankEnvironmentalRisk,
                                              `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_5_RankEnvironmentalRiskSUMNDC <- sum(WANDA_NDC$Q4_5_RankEnvironmentalRiskREV, na.rm = TRUE)
Q4_5_RankEnvironmentalRiskSUMNDC
```

```{r}
WANDA_NDC$Q4_6_RankPreviousPregnanciesREV <- recode(WANDA_NDC$Q4_6_RankPreviousPregnancies,
                                                `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_6_RankPreviousPregnanciesSUMNDC <- sum(WANDA_NDC$Q4_6_RankPreviousPregnanciesREV, na.rm = TRUE)
Q4_6_RankPreviousPregnanciesSUMNDC
```

```{r}
WANDA_NDC$Q4_7_RankProtectiveFactorsREV <- recode(WANDA_NDC$Q4_7_RankProtectiveFactors,
                                              `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_7_RankProtectiveFactorsSUMNDC <- sum(WANDA_NDC$Q4_7_RankProtectiveFactorsREV, na.rm = TRUE)
Q4_7_RankProtectiveFactorsSUMNDC
```

```{r}
WANDA_NDC$Q4_8_RankInterventionsWomenREV <- recode(WANDA_NDC$Q4_8_RankInterventionsWomen,
                                               `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_8_RankInterventionsWomenSUMNDC <- sum(WANDA_NDC$Q4_8_RankInterventionsWomenREV, na.rm = TRUE)
Q4_8_RankInterventionsWomenSUMNDC
```

```{r}
WANDA_NDC$Q4_9_RankInterventionsPartnersREV <- recode(WANDA_NDC$Q4_9_RankInterventionsPartners,
                                                  `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_9_RankInterventionsPartnersSUMNDC <- sum(WANDA_NDC$Q4_9_RankInterventionsPartnersREV, na.rm = TRUE)
Q4_9_RankInterventionsPartnersSUMNDC
```

```{r}
WANDA_NDC$Q4_10_RankHealthOutcomesWomenREV <- recode(WANDA_NDC$Q4_10_RankHealthOutcomesWomen,
                                                 `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_10_RankHealthOutcomesWomenSUMNDC <- sum(WANDA_NDC$Q4_10_RankHealthOutcomesWomenREV, na.rm = TRUE)
Q4_10_RankHealthOutcomesWomenSUMNDC
```

```{r}
WANDA_NDC$Q4_11_RankHealthOutcomesPartnersREV <- recode(WANDA_NDC$Q4_11_RankHealthOutcomesPartners,
                                                    `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_11_RankHealthOutcomesPartnersSUMNDC <- sum(WANDA_NDC$Q4_11_RankHealthOutcomesPartnersREV, na.rm = TRUE)
Q4_11_RankHealthOutcomesPartnersSUMNDC
```

```{r}
WANDA_NDC$Q4_12_RankHealthOutcomesBabyREV <- recode(WANDA_NDC$Q4_12_RankHealthOutcomesBaby,
                                                `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_12_RankHealthOutcomesBabySUMNDC <- sum(WANDA_NDC$Q4_12_RankHealthOutcomesBabyREV, na.rm = TRUE)
Q4_12_RankHealthOutcomesBabySUMNDC
```

```{r}
WANDA_NDC$Q4_13_RankSocialEconomicREV <- recode(WANDA_NDC$Q4_13_RankSocialEconomic,
                                            `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_13_RankSocialEconomicSUMNDC <- sum(WANDA_NDC$Q4_13_RankSocialEconomicREV, na.rm = TRUE)
Q4_13_RankSocialEconomicSUMNDC
```

```{r}
WANDA_NDC$Q4_14_RankParentInfantRelREV <- recode(WANDA_NDC$Q4_14_RankParentInfantRel,
                                             `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_14_RankParentInfantRelSUMNDC <- sum(WANDA_NDC$Q4_14_RankParentInfantRelREV, na.rm = TRUE)
Q4_14_RankParentInfantRelSUMNDC
```

```{r}
WANDA_NDC$Q4_15_RankParentParentRelREV <- recode(WANDA_NDC$Q4_15_RankParentParentRel,
                                             `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1)
Q4_15_RankParentParentRelSUMNDC <- sum(WANDA_NDC$Q4_15_RankParentParentRelREV, na.rm = TRUE)
Q4_15_RankParentParentRelSUMNDC
```
